Using Genetic Algorithms to Optimize the Analogue Method for Precipitation Downscaling in the Swiss Alps

### 2016-01-28 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Addition of plots for the CRPSS and the CRPS components.

\begin{table}[htb]
	\caption{Same as Table \ref{table:scores}, but expressed as the CRPSS improvement (\%) compared to the reference methods. For 4Zo, the improvement is relative to the reference method on the atmospheric circulation (2Z, Table \ref{table:params_R1}). For 4Zo-2MIo and 4Zo-4MIo, the improvement is relative to the reference method on the circulation and moisture variables (2Z-2MI, Table \ref{table:params_R2}).}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccccc}
			\hline 
			ID & \multicolumn{2}{c}{4Zo} & \multicolumn{2}{c}{4Zo-2MIo} & \multicolumn{2}{c}{4Zo-4MIo} \\ 
			& CP & VP & CP & VP & CP & VP \\ 
			\hline 
			1 & 13.6 & 13.0 & 11.9 & 9.9 & 12.8 & 9.6 \\
			2 & 13.3 & 7.5 & 11.2 & 9.4 & 12.5 & 10.8 \\
			3 & 12.2 & 9.0 & 13.2 & 12.0 & 14.1 & 13.5 \\
			4 & 14.2 & 10.5 & 12.4 & 10.6 & 14.5 & 12.5 \\
			5 & 14.5 & 8.8 & 12.5 & 9.1 & 14.1 & 10.0 \\
			6 & 13.3 & 8.6 & 11.5 & 8.2 & 14.1 & 8.4 \\
			7 & 22.8 & 10.6 & 19.7 & 15.7 & 21.7 & 16.3 \\
			8 & 20.7 & 11.9 & 19.2 & 13.5 & 20.8 & 14.0 \\
			9 & 14.4 & 9.5 & 15.8 & 15.2 & 16.7 & 14.1 \\
			10 & 14.2 & 9.4 & 12.9 & 11.2 & 14.6 & 11.8 \\
			\hline
			av. & 15.3 & 9.9 & 14.0 & 11.5 & 15.6 & 12.1 \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:scores_diff}
\end{table}

@@

@@

>>>>

@@

\begin{figure}[htb]
	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrpss_4Zo.pdf}}
	\caption{CRPSS relative improvement of 4Zo compared to the reference methods 2Z (Table \ref{table:params_R1}) for the CP and the VP.}
	\label{fig:figure_dcrpss_4Zo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrps_comp_4Zo.pdf}}
	\caption{Changes in the CRPS components of 4Zo relatively to the total CRPS of the reference methods 2Z (Table \ref{table:params_R1}) for the CP and the VP.}
	\label{fig:figure_dcrps_comp_4Zo}
\end{figure}

@@

\begin{figure}[htb]
	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrpss_4Zo-2HIo.pdf}}
	\caption{CRPSS relative improvement of 4Zo-2HIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
	\label{fig:figure_dcrpss_4Zo-2HIo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrpss_4Zo-4HIo.pdf}}
	\caption{CRPSS relative improvement of 4Zo-4HIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
	\label{fig:figure_dcrpss_4Zo-4HIo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrps_comp_4Zo-2HIo.pdf}}
	\caption{Changes in the CRPS components of 4Zo-2HIo relatively to the total CRPS of the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
	\label{fig:figure_dcrps_comp_4Zo-2HIo}
\end{figure}
